Everthing you wanted to know about PanDA but were truly truly afraid to ask

### 2017-02-14 introduction.tex
Preparatory work to move definitions

\section{Introduction}\label{sec:intro}
The Large Hadron Collider (LHC) is created  to explore the fundamental  properties  of matter for the next decades. Since LHC start-up in 2009, the experiments has collected and distributed hundreds  of  petabytes  of  data worldwide to hundreds of computer centers. Thousands of physicists analyze petascale  data volumes daily. One of  the LHC experiments  the ATLAS  \cite{Aad:2008}  utilizes the PanDA  workload management system \cite{Maeno2011} (WMS) for distributed data processing and analysis. The ATLAS Computing model \cite{Atlas2005} is based on a Grid paradigm \cite{Foster:1998}, with multilevel, hierarchically distributed computing  and storage resources. Acronym  PanDa stands for Production  and Distributed Analysis, the system  has  been developed to meet growing ATLAS production and analysis requirements for a data-driven  workload  management system capable of operating at LHC data processing scale.
PanDA has a highly scalable architecture. Scalability  has been demonstrated in ATLAS through the rapid increase in usage over the past several years of operations, and is expected to meet the continuously growing number of jobs over the next decade. PanDA  was designed to have the flexibility to adapt to emerging computing  technologies in processing,  storage, networking  as well as the underlying software stack (middleware). This flexibility has also been successfully demonstrated through the past six years of evolving  technologies adapted by computing centers in ATLAS which span many continents and yet are seamlessly integrated into PanDA.
PanDA  manages a wide spectrum of workloads, ranging from raw data processing to Monte Carlo simulation and user analysis, while actively evolving to meet rapidly changing science needs.  Today, it  serves several  thousand users, successfully managing job distribution to hundreds of ATLAS sites with more than 100,000 CPU cores  which process  more than a million jobs per day, Figure 1 shows  a  summary   of daily completed jobs on ATLAS Grid for the past 12 month.
\begin{figure}
\begin{center}
\includegraphics[width=\columnwidth]{figures/DailyJobs.png}
\caption{Daily completed jobs on ATLAS Grid\label{fig:daily}}
\end{center}
\end{figure}

>>>>

\section{Introduction}\label{sec:intro}

The Large Hadron Collider (LHC) is created to explore the fundamental properties
of matter for the next decades. Since LHC start-up in 2009, the experiments
collected and distributed hundreds of petabytes of data worldwide to hundreds of
computer centers. Thousands of physicists analyze petascale data volumes daily.
One of the LHC experiments, the ATLAS~\cite{Aad:2008}, utilizes the Production
and Distributed Analysis (PanDA) workload management system~\cite{Maeno2011}
(WMS) for distributed data processing and analysis. The ATLAS Computing
model~\cite{Atlas2005} is based on a Grid paradigm~\cite{Foster:1998}, with
multilevel, hierarchically distributed computing and storage resources. PanDA
has been developed to meet growing ATLAS production and analysis requirements
for a data-driven workload management system capable of operating at LHC data
processing scale.

PanDA has a highly scalable architecture. Scalability has been demonstrated in
ATLAS through the rapid increase in usage over the past several years of
operations, and PanDA is expected to meet the continuously growing computing
requirements of ATLAS over the next decade. PanDA was designed to have the
flexibility to adapt to emerging computing technologies in processing, storage,
networking as well as the underlying software stack. This flexibility has also
been successfully demonstrated through the past six years: computing centers in
ATLAS, spanning many continents, were seamlessly integrated into PanDA\@.

PanDA manages a wide spectrum of workloads, ranging from raw data processing to
Monte Carlo simulation and user analysis, while constantly evolving to meet
rapidly changing science needs. Today, PanDA serves several thousand users,
managing job distribution to hundreds of ATLAS sites with more than 100,000 CPU
cores which process more than a million jobs per day (Figure~\ref{fig:daily}).

\begin{figure}
    \begin{center}
        \includegraphics[width=\columnwidth]{figures/DailyJobs.png}
        \caption{Daily completed jobs on ATLAS Grid for the past 12 month}
    \end{center}
\label{fig:daily}
\end{figure}

In this paper, we describe how PanDA has been engineered to execute a specific
stage of the ATLAS Monte Carlo workflow on Titan, the larger high-performance
computing HPC system currently available in the USA\@.\mtnote{Explain the
benefits offered by Titan in terms of multithreading per node and possibly large
amount of concurrent nodes. Introduce also the notion of backfill.} This extends
the scope of PanDA's compute model, integrating both high-throughput and
high-performance computing resources and enabling the concurrent execution of
both  single and multi-core jobs. The integration of PanDA and Titan went
through three main engineering phases: (i) feasibility study and rapid
prototyping of an initial solution; (ii) progressing scaling of the  prototype
to saturate the available resources; (iii) study of a product-grade architecture
for generic HPC resources. Both phase i and ii have been completed enabling the
execution of up to eight million jobs a week on Titan. A prototype has been
engineered to support phase iii and experimental data are being collected.

In the next section we introduce \ldots.
